---
title: "Cabbages"
author: "Kimberly Aldana"
date: "June 5 2023"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

## Now with ggplot - first select the basic data
```{r}
library(ggplot2)

# Create the box plot
ggplot(veggy, aes(x = Cult, y = VitC)) +
  geom_boxplot() +
  labs(x = "Cult", y = "VitC") +
  ggtitle("Box Plot of VitC by Cult") +
  theme(plot.title = element_text(hjust = 0.5, size = 16))
```
 
 If you look at the two boxes on the box plot, the major box is above the lower one. The middle 50% of the method of higher box is quite a bit different between C39 and C52. These are complete apart from each other. We think we will find a statistical difference within these 2 methods.
 
### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
favstats(VitC~Cult,data=veggy)
```

  The average amount of Vitamin 39 is 51. The average amount of vitamin C52 is 64.5. Box C52 and Box C39 have no overlapping. The numerical difference is stated in the amounts.


## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
```{r}
t.test(VitC~Cult,data=veggy)
```
  The probability of getting a result as we just obtain is .000000003405, which is a small number. Which is the result of what we got. Comparing C39 and C52, the vitamin is so low. It is possible that it might happen but it is very low probability. The hypothesis is to be rejected. The method is difference.

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
